A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-05 paper.tex
Add TA structure figure

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

@@

Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator\cite{TA}. Where Ethereum client is used to interact with Ethereum and Tangle-accelerator is a caching proxy server for IOTA, which can serve thousands of IOTA requests at once without accessing remote IOTA full nodes frequently and provide PoW acceleration. Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator. However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{ta_structure}
    \caption{The structure of Tangle-accelerator.}
    \label{fig:ta_struct}
\end{figure}

>>>>

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{ta_structure}
    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration. It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed. Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
    \label{fig:ta_struct}
\end{figure}

@@

Therefore, transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator\cite{TA}. Where Ethereum client is used to interact with Ethereum and Tangle-accelerator is a caching proxy server for IOTA, which can serve thousands of IOTA requests at once without accessing remote IOTA full nodes frequently and provide PoW acceleration. However, MAM operations still cost a considerable time that improving the performance of MAM is an essential issue that needs to be done for the next step.
